R Notebook

### 2020-09-01 Prep_code/nat_stories_prep.Rmd
try models with weak data exclusions
add analysis of original SPR nat stories

>>>>

all <- txl_translator %>% 
  left_join(ngram_translator, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word", "Word_In_Story_Num")) %>% 
  left_join(grnn_translator, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word", "Word_In_Story_Num")) %>%
  left_join(freq, by=c("Story_Num", "Sentence_Num","Word_In_Sentence_Num", "Word", "Word_In_Story_Num")) %>% 
  #filter(Word_In_Sentence_Num!=0) %>% 
  ungroup() %>% 
  write_rds("natural_stories_surprisals2.rds")
```
